\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{legalpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage[parfill]{parskip}
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{xcolor}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

\pagestyle{empty}
\renewcommand{\baselinestretch}{1.25}

\def\LayoutCheckField#1#2{#2 #1}

% Variables
\newcommand{\slug}{SLUGVARIABLE}

\begin{document}

\section*{\centering\underline{DATA SUBJECT ACTION REQUEST}}
In order to submit a request to exercise individual rights pursuant to the Data Protection Laws (as
defined below), please complete this form and send it to our privacy team at:
\href{mailto:support.\slug@zipoapps.com}{\textbf{support.\slug@zipoapps.com}}. 
Upon receipt of your completed request, we will process it and
respond within the timelines required under applicable Data Protection Laws.

For the purpose of this Data Subject Action Request, the "Data Protection Laws" means any
applicable data, privacy and security regulations that apply subject to your jurisdiction and shall
include, without limitations and solely where applicable the EU General Data Protection
Regulation ("\textbf{GDPR}") and the California Consumer Privacy Act of 2018 ("\textbf{CCPA}").

\textbf{PLEASE FILL IN THE INFORMATION BELOW, PLEASE PROVIDE ACCURATE INFORMATION
OTHERWISE WE WON’T BE ABLE TO CONTACT YOU AND PROVIDE YOU WITH THE SUPPORT YOU
ARE SEEKING:}

\textbf{Full Name:} \underline{\hspace{4cm}} \\
\textbf{Email Address:} \underline{\hspace{4cm}} \\
\textbf{Phone Number (optional):} \underline{\hspace{4cm}} \\
\textbf{Name of the App you are using (if applicable):} \underline{\hspace{4cm}} \\

\subsection*{ARE YOU THE DATA SUBJECT?}
\begin{Form}
\begin{tabular}{l}
	\CheckBox[height=3pt]{I am the Data Subject requesting action} \\
	\CheckBox[height=3pt]{I am not the Data Subject; however, I am acting on behalf of the Data Subject.} \\
	\hspace{18pt}
	I have written authority, which I enclose and attached to this letter herein.
\end{tabular}
\end{Form}

\subsection*{WHAT IS YOUR RELATIONSHIP WITH US?}
\begin{Form}
\begin{tabular}{l}
	\CheckBox[height=3pt]{Customer} \\
	\CheckBox[height=3pt]{User of our App and Services} \\
	\CheckBox[height=3pt]{Other} \\
\end{tabular}
\end{Form}
\vspace{11pt}

The personal data required by this form is necessary to enable ZipoApps Ltd. and its affiliated
companies and subsidiaries ("\textbf{Company}") to process your Data Subject Action Request and is
subject to our privacy policy: \href{https://zipoapps.com/\slug/privacy}{https://zipoapps.com/\slug/privacy}. The information you supply
will only be used for the purposes of identifying the personal data you are requesting and for
responding to your request, in accordance with the GDPR. It may be shared with our legal and
administrative teams based outside of the EEA, subject to the EU Standard Contractual clauses
for our intra-group transfers, and it will be stored securely until the relevant procedures are
completed.

In addition to the information set forth above, we may require additional information and
documentation depending on the nature of your request and your relationship with the Company.
If additional information is needed to verify your identity, we will contact you immediately. Any
identification documents sent to us should be transmitted through secure means of
communication and should be photocopies or scanned images (do not send the originals).

Further please note, according to the CCPA your rights only apply to the Personal Information
collected \textbf{12 months prior to the request and you are not entitled to submit more than 2
requests in a 12 months period}. If you wish to exercise your right to opt-out please review our
Do Not Sell Notice: \href{https://zipoapps.com/\slug/dns}{https://zipoapps.com/\slug/dns}.

\subsection*{PLEASE CHECK THE APPLICABLE BOX:}

\begin{Form}
	\begin{tabular}{l}
			\CheckBox[height=3pt]{The right to access} \\
			\CheckBox[height=3pt]{The right to rectification} \\
			\CheckBox[height=3pt]{The right to erasure} \\
			\CheckBox[height=3pt]{The right to restrict processing} \\
			\CheckBox[height=3pt]{The right to receive information of why and how you are processing my information} \\
			\CheckBox[height=3pt]{The right to data portability} \\
			\CheckBox[height=3pt]{The right to receive a copy} \\
		  \CheckBox[height=3pt]{The right to object} \\
			\CheckBox[height=3pt]{The right not to be subject to decisions based solely on automated decisiion-making} \\
			\CheckBox[height=3pt]{Other} \\
	\end{tabular}
\end{Form}

\subsubsection*{Substantiate the request - please provide additional information about your request:}
\emph{Please provide as much detail as possible, such as relevant dates, references, etc. For further
information regarding the rights of individuals in relation to their personal data, please see our
Privacy policy}

\vspace{15pt}
\hrule
\vspace{15pt}
\hrule
\vspace{15pt}
\hrule
\vspace{23pt}

Please note that if you are making a Data Subject Action Request and the information you request
reveals details directly or indirectly about another person, we will need to seek the consent of
that person before we can disclose that information to you. In certain circumstances, where
disclosure of part or all of the information you have requested would adversely affect the rights
and freedoms of others, we may not be able to disclose the information to you, in which case you
will be informed promptly and given full reasons for that decision. Please further note that
information covered by a legal professional privilege or obligation cannot be disclosed.

\textbf{Thank you for filling in the form, please send it to: \\
\href{mailto:support.\slug@zipoapps.com}{support.\slug@zipoapps.com}. We will process
the request by the time specified in the Data Protection Laws. In most circumstances, we will
provide you the information requested free of charge. However, we may be permitted to charge
a reasonable fee if a Data Subject Action Request is repetitive or manifestly unfounded or
excessive. We also may charge a reasonable fee to comply with Data Subject Action Requests
for further copies of the same information.}

\subsubsection*{WHAT HAPPENS NEXT?}
If your request is valid, we will acknowledge your request in writing and provide you with a
reference number relating to your Data Subject Action Request and start processing your records.
If your request is valid but we are unable to identify you, we will advise you of this an
additional information. Once we have all the required information, your request should be
completed as set forth above and subject to Data Protection Law requirements and obligations. 

\end{document}
